ES Models: Random Forest

### 2025-04-01 docs/randomforest_kl.Qmd
new results data

    # wfs0 <- readRDS("data/old/wfs_lsm.rds")
      wfs <- readRDS("data/allresults_20250308.rds")

@@

    if(file.exists("data/ES-RF.RDA")) load("data/ES-RF.RDA")

>>>>

    # wfs0 <- readRDS("data/old/wfs_lsm.rds")
      wfs <- readRDS("data/old/allresults_20250308.rds")

@@

    if(file.exists("data/old/ES-RF.RDA")) load("data/old/ES-RF.RDA")
